### 2016-01-24 AssignmentX/Assignment10-Ditz_Schroeder-WS15-16.tex
added all data for ex 2 Assignment 10

\section*{Practical Assignment - \textit{Assemble the human mitochondrial genome}}

>>>>

\section*{Practical Assignment - \textit{Assemble the human mitochondrial genome}}
\subsubsection*{Introduction}
The mitochondrial genome is rather a small genome in our world. But even this rather small genome, with its $10^4$ basepairs is a though nut, when trying to discover its sequence from reads \cite{!!!!}. For this purpose we used two different alignment algorithms. The Velvet algorithm by Zebrino and Birney is using de Bruijn graphs to assemble the reads.\cite{VelvetProgram}
Likewise does the SOAP algotihm by Luo et al. use a de Bruijn graph \cite{SOAPProgram}. The differences of both algorithms lie in their detailed structure.

\subsubsection*{Results}
both algorithms were used to calculate the assembly of the mitochondrial genome seperatley. The velvet algorithm was computed on the homesource with 4 k-mer sizes (from 7 to 31 bases). as a result of the lacking hardware and the missing password for the WSI-Server, the resulting data from the SOAP algorithm was thankfully provided by Sanja Koehlers goup.

\subsubsection*{Discussion}

\subsubsection*{Acknowledgement}
Thanks again to Sanja Koehler an her group, who enabled this phenomenal sucess of publishing this paper.

\begin{thebibliography}{20}
	\bibitem{VelvetProgram} Velvet: algorithms for de novo short read assembly using de Bruijn graphs. D.R. Zerbino and E. Birney. Genome Research 18:821-829. 
	\bibitem{SOAPProgram} SOAPdenovo2: an empirically improved memory-efficient short-read de novo assembler. Luo et al. GigaScience 2012 1:18.
\end{thebibliography}
